Computational musicology, ????, Profit

### 2016-07-24 paper.tex
Iterate on the paradigm stuff.

Computational musicology is unusual in that it transgresses the barrier between what C. P. Snow called the two cultures of academia
- the sciences and the humanities\cite{Two Cultures}. Programming has conventionally been placed with the sciences, yet music is a
creative endevour usually understood as part of the humanities. In order to understand how computational musicology might
contribute to music, we have to examine this paradox.

Amnon Eden classifies the way that computer scientists think about their craft into rationalist, technocratic and scientific paradigms\cite{Three Paradigms}.
These conceptual models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
produce knowledge, but all three belong to Snow's scientific culture. None value or use literary methods.

@@

Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music Mind and Meaning}.

@@

This paper/essay attempts to resolve the tension that Minsky observed between a scientific and cultural approach to musical study
by beginning with complexity theory and then building upon that to consider literary and musical works. The informal and literary
styles is not just for fun (though I hope that it is that), but is also attempt to show how computational musicology might
function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.

@@

As an artform, music is an ideal subject for complexity analysis. Other media can also engage with complexity theory, but
few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' themselves through
Kolmogorov's lens.

>>>>

Computational musicology is unusual in that it transgresses the barrier between what C. P. Snow called the two cultures of academia
- the scientific and the literary\cite{Two Cultures}. Programming has conventionally been placed with the sciences, yet music is a
creative endevour usually understood as part of the humanities. In order to understand how computational musicology might
contribute to music, we have to examine this paradox.

Amnon Eden classifies the way that computer scientists conceptualise their craft into rationalist, technocratic and scientific paradigms\cite{Three Paradigms}.
These models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
produce knowledge, but all three belong to Snow's scientific culture. None value or use literary methods.

@@

Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He observes that computational
musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music Mind and Meaning}.

@@

Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
to understand the
past and evolution of species", music lacks a corresponding natural object for them to base their research
upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
to make their work "scientifically sound".

This paper/essay however, attempts to resolve the tension that Minsky observed between a scientific and cultural approach to
musical study by beginning with complexity theory and then building upon that to consider literary and musical works. The
informal and literary style is not just for fun (though I hope that it is that), but is also attempt to show how computational
musicology might function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.

@@

As an artform, music is an ideal subject for complexity analysis. Other media can also engage with complexity theory, but
few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
of algorithmic creation, but it would be difficult to analyse `Contact' and `The Library of Babel' themselves through
Kolmogorov's lens.
